### 2020-01-20 paper/sex_selection_spacing-ver3.tex
Remove pps graph for 4th spell for highest education

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
\setcounter{subfigure}{1}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
\setcounter{subfigure}{3}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_highest_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{4}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_highest_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{
Survival curves conditional on progression to next birth for urban women with eight or
more years of education; start point is nine months after prior birth
}
\label{fig:pps_high}
\end{figure}

>>>>

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
\setcounter{subfigure}{1}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
% \\
% \rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
% \setcounter{subfigure}{3}
% \subfloat[1972--1984]{
%     \begin{minipage}{0.46\textwidth}
%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_highest_urban_pps}} 
%         \captionsetup[subfigure]{labelformat=parens}
%     \end{minipage}
% } 
% \setcounter{subfigure}{4}
% \subfloat[2005--2016]{
%     \begin{minipage}{0.46\textwidth}
%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_highest_urban_pps}} 
%         \captionsetup[subfigure]{labelformat=parens}
%     \end{minipage}
% } 
% \caption{
% Survival curves conditional on progression to next birth for urban women with eight or
% more years of education; start point is nine months after prior birth
% }
\label{fig:pps_high}
\end{figure}
